Empirical normative theories

### 2020-08-03 simple.tex
Slight rework proof with factorisation of a lemma

Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the $\di(\ar) \subseteq \powersetz{\alldargs}$ as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \land \args \ibeats \ar}$. It represents the coalitions of fragments required to defend $\ar$ (when arguing for $\phi$) from the point of view of $i$. 
The following proposition shows that these coalitions can be added to $\ar$, and will be useful for other results.
\begin{proposition}
	$\forall i \in I, \phi \in \gPhi, \ar \in \allargs: \dargs \in \di(\ar) ⇒ \emptyset ≠ \dargs \subseteq \df(\ar)$.
\end{proposition}
\begin{proof}
	Let us prove that $\forall \ar \in \allargs: \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar)} = \powersetz{\df(\ar)}$, from which the conclusion follows, and which can be useful to clarify the relationship between $\di(\ar)$ and $\df(\ar)$. Note that by definition of $\df(\ar)$, $\dargs \in \powersetz{\df(\ar)}$ iff $\emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar))$. 
	Thus, we have to prove that
	$\forall \dargs \subseteq \allargs$:
	\begin{equation}
		\exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \suchthat \dbeatsinv(\args) = \dargs ⇔ \emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar)).
	\end{equation}

@@

\begin{theorem}
	A normatively adequate and convincing empirical theory is valid.
\end{theorem}
\begin{proof}
	Given any $i \in I$ and $\phi \in \gPhi$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstost \phi$; the conclusion then follows thanks to normative adequacy.

	Lemma: if $\ar_0$ $i$-defends $\phi$, then $\ar_0 \nileadstost \phi ⇒ \exists \dargs \in \di(\ar_0)$.
	Consider any $\ar_0 \in \allargs$ such that $\ar_0$ $i$-defends $\phi$ and $\ar_0 \nileadstost \phi$. 
	By definition, $\ar_0 \nileadstost \phi$ means that $\exists \hist \in \allhist \suchthat \ar_0 \in \histend \land \hist \nileadstost \phi$.
	Define $\args = \gbeatsinv(\ar_0) \cap \hist$. Thus, $\args \ibeats \ar_0$.
	Also, because $\ar_0$ $i$-defends $\phi$, $\args ≠ \emptyset$. 
	Therefore, $\dbeatsinv(\args) \in \di(\ar_0)$.

	From this lemma, using convincingness, we deduce that $[\ar_0 \in \gargs \land \ar_0 \nileadstost \phi] ⇒ \exists \ar_2 \in \gargs \cap \dfp(\ar_0)$. That is because $\ar_0 \in \gargs ⇒ \ar_0$ $i$-defends $\phi$, by convincingness, and, considering any $\dargs \in \di(\ar_0)$ and $\ar_2 = \ar_0 + \dargs$, $\ar_2 \in \gargs$ by definition of $\gargs$ and $\ar_2 \in \dfp(\ar_0)$ because $\dargs \in \di(\ar_0) ⇒ \dargs \in \df(\ar_0)$.

	To prove the theorem, build a finite sequence of arguments in $\gargs$, starting with any $\ar_0 \in \gleadstoinv(\phi)$. Observe that $\ar_0 \in \gargs$. Given $k \in 2\N$, if $\ar_k \nileadstost \phi$, define $\ar_{k + 2}$ using the deduction following the lemma, obtaining $\ar_{k + 2} \in \gargs \cap (\dfp)^\frac{k + 2}{2}(\ar_0)$. 
	By definition of an empirical theory, $\exists k \in \N \suchthat (\dfp)^k(\ar_0) = \emptyset$, thus, this process ends with some $\ar$ such that $\ar \ileadstost \phi$.
\end{proof}

\subsection{Effectively comparing models}
\begin{lemma}
	\label{th:produce}
	Given $\phi \in \Phi$, $\ar_0 \in \allargs$ that $i$-defends $\phi$, and $\hist \nileadstost \phi$ with $\ar_0 \in \histend$, define $\args =  \gbeatsinv(\ar_0) \cap \hist$, $\dargs = \dbeatsinv(\args)$, and $\ar_2 = \ar_0 + \dargs$. Then, $\ar_2 \in \gargs \cap \dfp(\ar_0)$.
\end{lemma}
\begin{proof}
	Because $\dargs \in \di(\ar_0)$.
\end{proof}

Given $\phi \in \Phi$ and two empirical theories $\gamma$ and $\delta$ for a given normative theory, say that they disagree about $\phi$ iff $\phi \in \gPhi[\gamma] \land ¬\phi \in \gPhi[\delta]$. Say that they are incompatible iff there is at least one $\phi \in \Phi$ that they disagree about.

>>>>

Given $i \in I, \phi \in \gPhi, \ar \in \allargs$, define the $\di(\ar) \subseteq \powersetz{\alldargs}$ as $\di(\ar) = \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \land \args \ibeats \ar}$. It represents the coalitions of fragments required to defend $\ar$ (when arguing for $\phi$) from the point of view of $i$. 
The following proposition shows that these coalitions can be added to $\ar$, and will be useful for other results.
\begin{proposition}
	\label{th:indf}
	$\forall i \in I, \phi \in \gPhi, \ar \in \allargs: \dargs \in \di(\ar) ⇒ \emptyset ≠ \dargs \subseteq \df(\ar)$.
\end{proposition}
\begin{proof}
	Let us prove that $\forall \ar \in \allargs: \set{\dbeatsinv(\args) \suchthat \emptyset ≠ \args \subseteq \gbeatsinv(\ar)} = \powersetz{\df(\ar)}$, from which the conclusion follows, and which can be useful to clarify the relationship between $\di(\ar)$ and $\df(\ar)$. Note that by definition of $\df(\ar)$, $\dargs \in \powersetz{\df(\ar)}$ iff $\emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar))$. 
	Thus, we have to prove that
	$\forall \dargs \subseteq \allargs$:
	\begin{equation}
		\exists \emptyset ≠ \args \subseteq \gbeatsinv(\ar) \suchthat \dbeatsinv(\args) = \dargs ⇔ \emptyset ≠ \dargs \subseteq \dbeatsinv(\gbeatsinv(\ar)).
	\end{equation}

@@

\begin{lemma}
	\label{th:produce}
	Given $\phi \in \gPhi$, $\ar_0 \in \gargs$ that $i$-defends $\phi$, and $\hist \nileadstost \phi$ with $\ar_0 \in \histend$, define $\args =  \gbeatsinv(\ar_0) \cap \hist$, $\dargs = \dbeatsinv(\args)$, and $\ar_2 = \ar_0 + \dargs$. Then, $\ar_2 \in \gargs \cap \dfp(\ar_0)$.
\end{lemma}
\begin{proof}
	By definition of $\ibeats$, $\args \ibeats \ar_0$.
	Also, because $\ar_0$ $i$-defends $\phi$, $\args ≠ \emptyset$. 
	Therefore, $\dargs \in \di(\ar_0)$.
	It follows that $\dargs \in \df(\ar_0)$, by \cref{th:indf}, and that $\ar_2 \in \dfp(\ar_0)$, by definition of $\dfp$. It also follows that $\ar_2 \in \dip(\ar_0)$, hence, that $\ar_2 \in \gargs$.
\end{proof}

\begin{theorem}
	A normatively adequate and convincing empirical theory is valid.
\end{theorem}
\begin{proof}
	Given any $i \in I$ and $\phi \in \gPhi$, suffices to show that for some $\ar \in \allargs$, $\ar \ileadstost \phi$; the conclusion then follows thanks to simple normative adequacy (equivalent to normative adequacy thanks to \cref{th:normeqsnorm}).

	Lemma: $[\ar_0 \in \gargs \land \ar_0 \nileadstost \phi] ⇒ \exists \ar_2 \in \gargs \cap \dfp(\ar_0)$. That is because $\ar_0 \in \gargs ⇒ \ar_0$ $i$-defends $\phi$, by convincingness, and,
	by definition, $\ar_0 \nileadstost \phi$ means that $\exists \hist \in \allhist \suchthat \ar_0 \in \histend \land \hist \nileadstost \phi$; \cref{th:produce} thus applies.

	To prove the theorem, build a finite sequence of arguments in $\gargs$, starting with any $\ar_0 \in \gleadstoinv(\phi)$. Observe that $\ar_0 \in \gargs$. Given $k \in 2\N$, if $\ar_k \nileadstost \phi$, define $\ar_{k + 2}$ using the above lemma, obtaining $\ar_{k + 2} \in \gargs \cap (\dfp)^\frac{k + 2}{2}(\ar_0)$. Continue applying the lemma and producing further arguments as long as $\ar_k \nileadstost \phi$.
	By definition of an empirical theory, $\exists k \in \N \suchthat (\dfp)^k(\ar_0) = \emptyset$, thus, this process ends with some $\ar$ such that $\ar \ileadstost \phi$.
\end{proof}

\subsection{Effectively comparing models}
Given $\phi \in \Phi$ and two empirical theories $\gamma$ and $\delta$ for a given normative theory, say that they disagree about $\phi$ iff $\phi \in \gPhi[\gamma] \land ¬\phi \in \gPhi[\delta]$. Say that they are incompatible iff there is at least one $\phi \in \Phi$ that they disagree about.
